### 2014-03-14 paper/designspace.tex
new figures!  well, still using placeholders, but templated now, anyway.  also, added star and tree to tubespace figure

We propose the use of tubes to redirect active components through the core and onto the surface of 3D printed interactive objects.  By using different types and topologies of tubes and inserting different media into the completed tubes, a variety of input and output types \valkyrie{need clearer word than ``types"} can be located at arbitrary points on the surface of a 3D print.  We describe the design space of tubes, and then follow up with some of the input and output possibilities---both those that have been previously explored and those that are possible but remain unexplored.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/series-of-tubes.jpg}
\caption{This box (a) contains an enclosed Helmholz resonator, seen in the cutaway view (b).  This resonator creates a sound when air is blown through the tube at the top, because air compresses at the small neck joint between the chamber and the tube.  \valkyrie{need to get a test print of this that actually works}}
\label{fig:ocarina}
\end{figure}

>>>>

We propose the use of tubes to redirect active components through the core and onto the surface of 3D printed interactive objects.  By using different types and topologies of tubes and inserting different media into the completed tubes, a variety of inputs and outputs can be located at arbitrary points on the surface of a 3D print.  We describe the design space of tubes, and then follow up with some of the input and output possibilities---both those that have been previously explored and those that are possible but remain unexplored.

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/helmholz.png}
\caption{This box (a) contains an enclosed Helmholz resonator, seen in the cutaway view (b).  This resonator creates a sound when air is blown through the tube at the top, because air compresses at the small neck joint between the chamber and the tube.  \valkyrie{need to get a test print of this that actually works}}
\label{fig:ocarina}
\end{figure}
